```{r}
library(knitr)
library(tidyverse)
library(janitor)
library(lubridate) 
library(here) 
library(sf) 
library(tmap)
library(tidycensus)
```

```{r}
bikeshare <- df <- read_csv(here("data_raw", "202209-capitalbikeshare-tripdata.csv"))
neigh=st_read(here("data_raw","dc_neigh.geojson")) %>% clean_names()
class(neigh)
```

```{r}
census_api_key("e20bbef4315eae437393461fd7f2b4126b419749")
```

```{r}
df_census=get_acs(geography = "tract",
                  variables=c("median_inc"="B06011_001"),
                  state="DC",geometry=TRUE,year=2018) 
```
```{r}

```
want to count rides, grouped by neighborhood

```{r}
df_cens=df_census %>% select(-moe) %>% spread(variable,estimate) 
```




point - 0-dimensional geometry containing a single point 
linestring - sequence of points connected by straight, non-self intersecting line pieces; one-dimensional geometry 
polygon

multipoint - bunch of points 
linestring - connected lines 
multilinestring - multiple disjoint collections of linestrings 
polygon - polygon 
multipolygon - multiple disjoint polygons
geometrycollection - mixture of all the other types in one plot


is there a correlation between income and ridership? 
is there a different temporal pattern for different income levels?
can we figure out income of people working in the area as opposed to living? 

tmap - density stuff? like per square mile, per blocks, density map that looks like topography
  can also use ggplot
use math for density distribution maybe?
